\LARGE HIV virulence evolution in structured epidemic models

### 2016-05-30 poster/hivlhs_eeid2016.Rnw
restructure poster; drop URLs from bib

\newlength{\shortcolumnheight}
\setlength{\shortcolumnheight}{75cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}
%\includegraphics[width=\textwidth]{images/photobanner.pdf}
\vspace{0.5cm}
  \noindent\begin{columns}
    % ---------------------------------------------------------%
    % Set up a column 
    \begin{column}{.33\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth}  % tweaks the width, makes a new \textwidth
          \parbox[t][\columnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

<<tradeoff_fig,echo=FALSE,fig.height=14,fig.width=30,out.width="0.95\\textwidth",dev="tikz",cache=TRUE,dependson="setup3">>=
print(gg_tradeoff)
@

@@

%%\vfill
\vspace{0.5cm}

@@

%\pichskip{15pt}% Horizontal gap between picture and text
%\parpic[l][t]{%
%  \begin{minipage}{0.6\textwidth}
    \includegraphics[width=0.55\textwidth]{images/LHScrop.png}
%  \end{minipage}
%}
%%  \end{center}
%\caption{}
%\end{wrapfigure}
\begin{itemize}
  \item Latin hypercube sampling: parameters from
    \cite{champredon_hiv_2013}
  \item parameters calibrated across models to the same \textbf{initial epidemic growth rate} ($r$)
\end{itemize}
\end{block}
}
\end{minipage}
\end{beamercolorbox}
\end{column}
    % ---------------------------------------------------------%
    % end the column

    % ---------------------------------------------------------%
    % Set up a column 
\begin{column}{.65\textwidth}
\begin{columns}
    \begin{column}{.5\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
          \parbox[t][\shortcolumnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

<<virdyn,dev="tikz",fig.width=25,fig.height=30,cache=TRUE,out.width="0.95\\textwidth">>=
ss <- subset(sum_list[["vir_mat"]],tvec<750)
ss$model <- factor(ss$model, c("random",
         "pairform+epc", "pairform","instswitch+epc","instswitch","implicit"))

gg_virtraj <- ggplot(ss,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
    geom_line(aes(colour=model,linetype=model),lwd=1)+
    geom_ribbon(aes(fill = model), alpha=0.3)+
    labs(x="time (years)",y=Lspvl) +
    theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
          axis.title.x = element_text(margin = margin(10,0,0,0))) +
    facet_wrap(~model, nrow = 3) +
    zero_margin+
    theme(legend.position="none")+
    scale_x_continuous(breaks=c(0,600))
print(gg_virtraj)
@

@@

\end{block}            
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{block}{Univariate summary}

<<univ,cache=TRUE,dev="tikz",fig.width=30,fig.height=30,out.width="0.95\\textwidth">>=
sL <- transform(sum_list[["sum_mat"]],rel_peak=peak_vir/eq_vir)
sL$model <- factor(sL$model, c("random","pairform+epc", "pairform", "instswitch+epc","instswitch" , "implicit"))
mL <- melt(sL,id.vars=c("model","run"))
## horrible hack (but doesn't help); subsample
## w <- which(mL$model=="random")
## mLw <- mL[-sample(w,size=length(w)*9/10,replace=FALSE),]
w <- with(mL,which(model=="random" & variable=="eq_vir"))
rval <- mean(mL$value[w])
mLw <- droplevels(mL[-w,])
mLw$variable <- fixfac2(mLw$variable)

gg_univ <- ggplot(mLw,aes(value,model,fill=model))+
    geom_violinh(width=1)+
    facet_wrap(~variable,scale="free_x")+
    guides(fill=guide_legend(reverse=TRUE))+
    labs(y="",x="")+
    geom_point(data=data.frame(model="random",
                               variable="equilibrium virulence",
                               value=rval),
               pch=22,size=8,show.legend=FALSE) +
    theme(legend.position="none")+
    zero_x_margin
print(gg_univ)
@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

}
         % ---------------------------------------------------------%
          % end the column
        \end{minipage}
      \end{beamercolorbox}
   \end{column}

    % ---------------------------------------------------------%
    % end the column
    \begin{column}{.5\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
          \parbox[t][\shortcolumnheight]{\textwidth}{ % must be some better way to set the the height, width and textwidth simultaneously
            % Since all columns are the same length, it is all nice and tidy.  You have to get the height empirically
            % ---------------------------------------------------------%
            % fill each column with content

\begin{block}{Bivariate summary}
<<ggfuns,echo=FALSE>>=
trim_gg <- function(gg,hack_spaces=TRUE) {
    n <- gg$nrow
    gg$nrow <- gg$ncol <- n-1
    v <- 1:n^2
    gg$plots <- gg$plots[v>n & v%%n!=0]
    gg$xAxisLabels <- gg$xAxisLabels[-n]
    gg$yAxisLabels <- gg$yAxisLabels[-1]
    ## ggpairs tries to parse labels, so this fails if they
    ## have spaces in them ... maybe there's a better way?
    if (hack_spaces) {
        gg$xAxisLabels <- gsub("_"," ",gg$xAxisLabels)
        gg$yAxisLabels <- gsub("_"," ",gg$yAxisLabels)
    }
    return(gg)
}

tweak_legends_gg <- function(gg,pos=1.5) {
    n <- gg$nrow
    for (i in 1:n) {
        for (j in 1:n) {
            inner <- getPlot(gg,i,j)
            if (i==1 & j==1) {
                inner <- inner + ggplot2::theme(legend.position=c(pos,0.5)) +
                    guides(colour = guide_legend(override.aes = list(size=6)))
            } else {
                inner <- inner + ggplot2::theme(legend.position="none")
            }
            gg <- putPlot(gg,inner,i,j)
        }
    }
    return(gg)
}

tweak_colours_gg <- function(gg) {
    n <- gg$nrow
    for (i in 1:n) {
        for (j in 1:n) {
            inner <- getPlot(gg,i,j)
            inner <- inner+scale_colour_brewer(palette = 'Dark2')
            gg <- putPlot(gg,inner,i,j)
        }
    }
    return(gg)
}
@

<<ggpairs,echo=FALSE,fig.width=10,fig.height=10>>=
sL2 <- sL
names(sL2)[na.omit(match(orig_sum_labs,names(sL)))] <- gsub(" ","_",new_sum_labs)
    ## paste0("`",new_sum_labs,"`")
ggp1 <- ggpairs(sL2,
        mapping = ggplot2::aes(color = model),
        columns=3:6,
        legends=TRUE,
        lower = list(continuous = wrap("points",size=0.1)), ## alpha = 0.3,size=0.5)),
        diag = list(continuous = "blankDiag"),
        upper = list(continuous = "blank"))
## http://stackoverflow.com/questions/14711550/is-there-a-way-to-change-the-color-palette-for-ggallyggpairs-using-ggplot
## have to change plot one panel at a time
ggp2 <- tweak_colours_gg(tweak_legends_gg(trim_gg(ggp1)))
## add 1-to-1 line
inner <- getPlot(ggp2,2,1)
inner <- inner+geom_abline(intercept=0,slope=1,lty=2)
ggp2 <- putPlot(ggp2,inner,2,1)
## tweak scale
inner <- getPlot(ggp2,3,1)
inner <- inner+scale_x_continuous(breaks=seq(2.5,4.5,by=0.5))
ggp2 <- putPlot(ggp2,inner,3,1)
print(ggp2,spacingProportion=0)
@

{\tiny
%% Add numbered references
\setbeamertemplate{bibliography item}[text]
%% Stop line breaks
\setbeamertemplate{bibliography entry title}{}
\setbeamertemplate{bibliography entry location}{}
\setbeamertemplate{bibliography entry note}{}
%% Stop font color changes
% \setbeamercolor*{bibliography item}{fg=black}
% \setbeamercolor*{bibliography entry title}{fg=black}
% \setbeamercolor*{bibliography entry author}{fg=black}
% \setbeamercolor*{bibliography entry location}{fg=black}
% \setbeamercolor*{bibliography entry note}{fg=black} 
%% Generate bibliography
\bibliographystyle{vancouver}
\bibliography{../ms/virulence}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \vspace{0.5cm}

}
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    \end{columns}
     \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
       \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
         \parbox[t][30cm]{\textwidth}{ % must be some better way to set

@@

ggplot(mL3,aes(LHSval,sumval,colour=model))+
    geom_point(pch=".",alpha=0.5)+
    facet_grid(sumvar~LHSvar,scales="free",
               labeller = L)+
    geom_smooth(se=FALSE)+labs(x="",y="")+
    ## leave a little extra room?
    scale_x_log10(expand=c(0,0.08),breaks=brkfun)+
    zero_margin
@
\end{block}
}
        \end{minipage}
    \end{beamercolorbox}
 \end{column}  % end right-hand 2/3 column
 \end{columns}  % end overall columns
\end{frame}
\end{document}

>>>>

\newlength{\topcolumnheight}
\setlength{\topcolumnheight}{50cm}

\newlength{\bottomcolumnheight}
\setlength{\bottomcolumnheight}{30cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}
%\includegraphics[width=\textwidth]{images/photobanner.pdf}
  \vspace{0.5cm}
  \noindent
\begin{columns}
    % ---------------------------------------------------------%
  \begin{column}{.33\textwidth}
    \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
      \begin{minipage}[T]{.95\textwidth}
        \parbox[t][\columnheight]{\textwidth}{

@@

@@

\includegraphics[width=0.95\textwidth]{figure/tradeoff.pdf}

@@

@@

%\pichskip{15pt}% Horizontal gap between picture and text
%\parpic[l][t]{%
%  \begin{minipage}{0.6\textwidth}
    \includegraphics[width=0.55\textwidth]{images/LHScrop.png}
%  \end{minipage}
%}
%%  \end{center}
%\caption{}
%\end{wrapfigure}
\begin{itemize}
  \item Latin hypercube sampling: parameters from
    \cite{champredon_hiv_2013}
  \item parameters calibrated across models to the same \textbf{initial epidemic growth rate} ($r$)
\end{itemize}
\end{block}
}
\end{minipage}
\end{beamercolorbox}
\end{column}

\begin{column}{.65\textwidth}

\begin{columns}
  \begin{column}{.5\textwidth}
    \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
      \begin{minipage}[T]{.95\textwidth}
        \parbox[t][\topcolumnheight]{\textwidth}{

@@

\includegraphics[width=0.95\textwidth]{figure/virtraj.pdf}

@@

@@

        } % end parbox
        \end{minipage}
    \end{beamercolorbox}
  \end{column}

  \begin{column}{.5\textwidth}
    \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
      \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
        \parbox[t][\topcolumnheight]{\textwidth}{

            \begin{block}{Univariate summary}
              \includegraphics[width=0.95\textwidth]{figure/univ.pdf}
            \end{block}
            \vspace{0.5cm}

        } % end parbox
        \end{minipage}
      \end{beamercolorbox}
    \end{column}

\end{columns}

\begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
  \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
    \parbox[t][30cm]{\textwidth}{ % must be some better way to set

@@

ggplot(mL3,aes(LHSval,sumval,colour=model))+
    geom_point(pch=".",alpha=0.5)+
    facet_grid(sumvar~LHSvar,scales="free",
               labeller = L)+
    geom_smooth(se=FALSE)+labs(x="",y="")+
    ## leave a little extra room?
    scale_x_log10(expand=c(0,0.08),breaks=brkfun)+
    zero_margin
@
\end{block}
}
        \end{minipage}
    \end{beamercolorbox}

\begin{columns}
    \begin{column}{.5\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
          \parbox[t][\bottomcolumnheight]{\textwidth}{

\end{block}
}
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    \begin{column}{.5\textwidth}
      \begin{beamercolorbox}[center,wd=\textwidth]{postercolumn}
        \begin{minipage}[T]{.95\textwidth} % tweaks the width, makes a new \textwidth
          \parbox[t][\bottomcolumnheight]{\textwidth}{

{\tiny
%% Add numbered references
\setbeamertemplate{bibliography item}[text]
%% Stop line breaks
\setbeamertemplate{bibliography entry title}{}
\setbeamertemplate{bibliography entry location}{}
\setbeamertemplate{bibliography entry note}{}
%% Stop font color changes
% \setbeamercolor*{bibliography item}{fg=black}
% \setbeamercolor*{bibliography entry title}{fg=black}
% \setbeamercolor*{bibliography entry author}{fg=black}
% \setbeamercolor*{bibliography entry location}{fg=black}
% \setbeamercolor*{bibliography entry note}{fg=black} 
%% Generate bibliography
\bibliographystyle{vancouver}
\bibliography{../ms/virulence}
}
\end{block}

}
        \end{minipage}
      \end{beamercolorbox}
    \end{column}
    \end{columns}
 \end{column}  % end right-hand 2/3 column
 \end{columns}  % end 50/50 columns
\end{frame}
\end{document}
